### 2024-01-28 README.Rmd
add a couple of things

@@

>>>>

## Processing annotations

1. Process and tabulate the annotations. TODO: first local then containerized

```{r}

```

@@

1. Crop all annotations using the functions in the R package. TODO: first local then containerized (code now written for locals)

```{r, eval=FALSE}
# Read in the annotations
anns <- readRDS("data/objects/annotations_wide_noempty.rds")
rofcamtrap::crop_from_annotations(anns, 
                                  base_dir = "/media/vlucet/TrailCamST1/",
                                  out_dir = "data/images/cropped/")
```
